\clearpage
\section*{Appendix A. Detailed assessment of included studies}
\label{AppendixA}

\begingroup
\scriptsize
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{1.1}
\begin{center}
\begin{longtable}{p{1.5cm} p{4cm} p{2.0cm} c c c c c}
\caption{Quality assessment of the included studies}\label{tab:appendixA_single}\\
\hline
ID & Study & Authors & QA1 & QA2 & QA3 & QA4 & Total \\
\hline
\endfirsthead

\hline
ID & Study & Authors & QA1 & QA2 & QA3 & QA4 & Total \\
\hline
\endhead

\hline
\endfoot

\hline
\endlastfoot

\cite{fasoyinu2025} & Wearable sensing devices for construction safety: Research trends, applications, challenges, and future opportunities & Fasoyinu et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{wang2024} & Monitoring and evaluating the status and behaviour of construction workers using wearable sensing technologies  & Wang et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{anjum2025} & Generalizing fatigue prediction models for construction workers: Cross-experiment evaluation with transfer learning across thermal and load conditions & Anjum et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{cheng2025} & Automated fall risk classification for construction workers using wearable devices, BIM, and optimized hybrid deep learning & Cheng et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{kakhi2025} & Fatigue monitoring using wearables and AI: Trends, challenges, and future opportunities & Kakhi et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{umer2025} & Deep learning-based fatigue monitoring of construction workers using physiological signals & Umer et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{albarran2025} & Early detection of physical fatigue in industry using wearable sensors and contextual modeling & Morillo et al. & 1 & 1 & 1 & 1 & 4 \\

\cite{karim2025} & Advancing physical and mental fatigue analysis in construction workers: Insights, technologies, and future directions & Karim et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{ojha2024} & Worker-centric heat strain analysis: Integrating physiological signals with ensemble learning and domain adaptation & Ojha et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{thomas2025} & IoT Wearable Devices to Detect and Monitor Mental Health and Stress & Thomas et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{goutham2025} & AI-Driven Fatigue Prediction in Healthcare Professionals Using Wearable Sensor Data and Gradient-Boosted Machine Learning Models & Goutham et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{sim2023} & Exploring Edge Machine Learning-based Stress Prediction using Wearable Devices & Sim et al. & 1 & 1 & 1 & 1 & 4 \\
\cite{he2025} & Towards a nuanced classification of mental fatigue: A comprehensive review & He et al. & 1 & 1 & 1 & 0.5 & 3.5 \\
\cite{elmousalami2025} & Electroencephalography (EEG) for psychological hazards and mental health in construction safety automation & Elmousalami et al. & 1 & 0.5 & 1 & 1 & 3.5 \\
\cite{jaros2025} & Automated recognition of worker activity using machine learning and multi-sensor fusion & Jaros et al. & 1 & 1 & 0.5 & 1 & 3.5 \\

\cite{kazar2021} & Exploring the relations between the physiological factors and the likelihood of accidents on construction sites & Kazar et al. & 1 & 0.5 & 1 & 1 & 3.5 \\
\cite{singh2025} & AI-Powered Mental Health Tracking With Smartwatch Integration for Instantaneous Stress Assessment and Assistance & Singh et al. & 1 & 1 & 1 & 0.5 & 3.5 \\
\cite{mohapatra2024} & Wearable network for multilevel physical fatigue prediction in manufacturing workersn & Mohapatra et al. & 1 & 1 & 1 & 0.5 & 3.5 \\
\cite{chen2025} & Biosignal measurement for human-robot collaboration in construction & Chen et al. & 1 & 0 & 1 & 1 & 3 \\
\cite{ardecani2025} & Assessing workers’ neuro-physiological stress reSpO & Ardecani et al. & 1 & 0.5 & 1 & 0.5 & 3 \\
\cite{xianyong2025} & Wearable smart sensors integration with AI and machine learning for tracking human health & Shi et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{abuwarda2022} & Wearable devices: Cross benefits from healthcare to construction & Abuwarda et al. & 1 & 0 & 1 & 1 & 3 \\
\cite{dhanasekar2025} & NeuroAdapt: A Multimodal Emotion-Cognitive-Fatigue Adaptive BCI System for Robotic Upper-Limb Rehabilitation  & Dhanasekar et al. & 1 & 1 & 1 & 0 & 3 \\

\cite{aishwarya2024} & Multi-Purpose Wearable Biofeedback Accessories - 2024 International Conference on Power, Energy, Control and Transmission Systems & Aishwarya et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{kuzhaloli2025} & Wearable Tech for Mental Health Monitoring Real-Time Stress Detection Using Biometric Sensors  & Kuzhaloli et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{arya2024} & Effective Driver Fatigue Management and Prevention Using Cloud-Integrated RNN Models & Arya et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{subathra2025} & A Wearable Electronic Band for Stress Understanding Using Machine Learning & Subathra et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{karpagam2024} & Physiological Data-Based Stress Detection: From Wrist Sensors to Cloud Computing and User Feedback Integration & Karpagam et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{narayana2025} & IoT-Enabled Health Monitoring Glove with Machine Learning-Based Risk Classification & Narayana et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{jayaweera2020} & An Integrated Framework for Predicting Health Based on Sensor Data Using Machine Learning  & Jayaweera et al. & 1 & 1 & 1 & 0 & 3 \\

\cite{rajas2025} & IoT-based Mental Health Monitoring with Machine Learning  & Rajas et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{devi2023} & Wearable Physiological IoT System with Neural Network to Detect an Individual IT Professional’s Stress / Emotion in Working Environments & Devi et al. & 1 & 1 & 1 & 0 & 3 \\
\cite{divyabharathi2025} & An Explainable IoT-based Framework for Anomaly Detection and Emergency Decision Management in Smart Healthcare  & Divyabharathi et al. & 1 & 1 & 0.5 & 0 & 2.5 \\
\cite{kiriti2022} & Smart band for senior citizens & Kiriti et al. & 1 & 1 & 0.5 & 0 & 2.5 \\
\cite{vinusha2023} & Smartwatch-based Vomiting Sensation Detection using Heart Rate Analysis and Metaverse Integration  & Vinusha et al. & 1 & 1 & 0 & 0 & 2 \\
\cite{devi2025} & IoT intelligent watch for child safety & Devi et al. & 1 & 1 & 0 & 0 & 2 \\

\cite{sanjeevi2024} & Smart heart monitor using machine learning & Sanjeevi et al. & 1 & 1 & 0 & 0 & 2 \\

\end{longtable}
\end{center}
\endgroup


